### 2014-08-25 tex/proofs.tex
Fixed some typos in the rules, added additional condition summarization semantics to the summarize rule

%I'm wondering... do we use this theorem anywhere? I think the place we needed it got re-structured, am I right?
\begin{theorem}
\label{thm:colex}
If we have a summary state $s_s = ( \cfgnt{L}_s\ \cfgnt{R}_s\ \phi_s\ \eta_s\ \cfgnt{e}_s\ \cfgnt{k}_s )$, then for any reference $r \in \cfgnt{L}_s^\leftarrow$, 
$$\bigvee \{ \phi \mid (\phi\ \cfgnt{l})\in \cfgnt{L}_s (\cfgnt{r})\} = \cfgt{true}$$
\end{theorem}
\begin{proof}
The proof will proceed inductively.

@@

\end{proof}
%\begin{lemma}
%\label{lem:ref}
%For any symbolic state $s_s$, constraint $\phi$, and stack reference $\cfgnt{r}$ such that $(\phi\ \ell) \in \cfgnt{L}_s (\cfgnt{r})$, then 
%\begin{equation}
%\exists \Gamma_n^s\ ( \phi = \mathbb{PC} (\Gamma_n^s) )
%\end{equation}
%\end{lemma}
%\begin{proof}
%\end{proof}
%
%\begin{lemma}
%\label{lem:path}
%If there is some access path $\Gamma_n^s$ in state $s_s$ such that $\mathbb{S}(\phi_s \wedge \mathbb{PC}(\Gamma_n^s))$, then $\Gamma_n^\ell$ is an access path in some lazy state $s_\ell$ such that $s_\ell \sqsubset s_s$
%\end{lemma}
%\begin{proof}
%\end{proof}

@@

\begin{theorem}
If we have some initial state $s_0$, and we apply the summary state transition function n times in order to get a sequence of summary states $\Pi_n^s$, then the following statement is true:
\begin{equation}
\mathit{last}(\Pi_n^s) \cong \mathbb{FS}(\rightarrow_\ell, s_0, \mathbb{CF}(\Pi_n^s) )
\end{equation}
\end{theorem}
\begin{proof}
The proof will proceed inductively.

Base case: The initial state is exact. (hands waving)

Inductive step: If summary state $s_s$ is exact, then any state $s_s^\prime$ such that $s_s \rightarrow_s s_s^\prime$ is also exact. Suppose $s_s$ has the form for a field read, field write, or reference compare rule. By Lemmas \ref{lem:access}, \ref{lem:write}, and \ref{lem:compare}, $s_s^\prime$ will also be exact.

>>>>

\begin{comment}
%I'm wondering... do we use this theorem anywhere? I think the place we needed it got re-structured, am I right?
\begin{theorem}
\label{thm:colex}
If we have a summary state $s_s = ( \cfgnt{L}_s\ \cfgnt{R}_s\ \phi_s\ \eta_s\ \cfgnt{e}_s\ \cfgnt{k}_s )$, then for any reference $r \in \cfgnt{L}_s^\leftarrow$, 
$$\bigvee \{ \phi \mid (\phi\ \cfgnt{l})\in \cfgnt{L}_s (\cfgnt{r})\} = \cfgt{true}$$
\end{theorem}
\begin{proof}
The proof will proceed inductively.

@@

\end{proof}
\end{comment}
%\begin{lemma}
%\label{lem:ref}
%For any symbolic state $s_s$, constraint $\phi$, and stack reference $\cfgnt{r}$ such that $(\phi\ \ell) \in \cfgnt{L}_s (\cfgnt{r})$, then 
%\begin{equation}
%\exists \Gamma_n^s\ ( \phi = \mathbb{PC} (\Gamma_n^s) )
%\end{equation}
%\end{lemma}
%\begin{proof}
%\end{proof}
%
%\begin{lemma}
%\label{lem:path}
%If there is some access path $\Gamma_n^s$ in state $s_s$ such that $\mathbb{S}(\phi_s \wedge \mathbb{PC}(\Gamma_n^s))$, then $\Gamma_n^\ell$ is an access path in some lazy state $s_\ell$ such that $s_\ell \sqsubset s_s$
%\end{lemma}
%\begin{proof}
%\end{proof}

@@

\begin{theorem}
If $\Pi_n^s$ is a feasible summary state sequence, then the final state in $\Pi_n^s$ is equivalent to the feasible set of lazy states sharing the same control flow sequence:
\begin{equation}
\mathit{last}(\Pi_n^s) \cong \mathbb{FS}(\rightarrow_\ell, \mathit{first}(\Pi_n^s), \mathbb{CF}(\Pi_n^s) )
\end{equation}
\end{theorem}
\begin{proof}
The proof will proceed inductively.

Base case: For any initial state $s_0$, the feasible state set reduces to $\{s_0\}$:
$$\mathbb{FS}(\rightarrow_\ell, s_0, \mathbb{CF}(s_0)) = \{s_0\}$$
It's obvious that a homomorphism from $s_0$ to $s_0$ exists, and that the Heap Constraint is always satisfiable by construction. Thus, $s_0 \in  s_0 \sqsubset s_0$.

Inductive step: If summary state $s_s$ is exact, then any state $s_s^\prime$ such that $s_s \rightarrow_s s_s^\prime$ is also exact. Suppose $s_s $ has the form for a field read, field write, or reference compare rule. By Lemmas \ref{lem:access}, \ref{lem:write}, and \ref{lem:compare}, $s_s^\prime$ will also be exact.
Suppose $s_s$ is accepted by the "new" rule. In this case, the new reference points to the new location on condition true, so it's obvious that $s_s$ represents all of the proper lazy states, and the existence of any infeasible lazy states represented by $s_s^prime$ would imply that $s_s$ is not exact.
For all the other rules, the L and R functions are unchanged, and the rules for the $\eta$, $e$, and $k$ are exactly the same between the lazy and summary machines, so there is a bijective mapping between the represented states in $s_s$ and $s_s^\prime$. 
Thus, in all cases, if $s_s$ is exact, then $s_s^\prime$ is also exact.

Having proved both the base case and the inductive step, the it follows that for any $n$, $s_n$ will be exact.
